### 2014-06-20 1_introduction/introduction.tex
auto

As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is Polarimetric SAR (POLSAR).
POLSAR is the natural extension of SAR, exploiting the natural polarization property of Electromagnetic (EM) waves.
It extends the SAR acquisition information from the traditional single
SAR channel to multi-channel POLSAR data, corresponding to a different combination of transmitted and received polarizations. Similar to the extension from black-and-white images to colour photography, the polarimetric extension brought about
multi-channel POLSAR data as compared to the traditional one-channel SAR data.

@@

Similarly speaking, heteroskedasticity poses numerous negative impacts on the usual framework of statistical estimation, which most of the time makes use of various different techniques and criteria known to work very well on the usual models.
For example, in modelling, it is very common to use subtractive differences to discriminate and to make decisional inferences. However, for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure.
Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criteria which is probably due to the Gauss Markov theorem.
For SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.

@@

 In
                another thread of study, to combat the negative
                impacts caused by multiplicative and heteroskedastic
                properties for SAR data, experienced researchers in the
                field have developed numerous ingenious ways to tackle
                these issues.
For
                example, when the sense of subtractive distance is not
                consistent for SAR data, the ratio is proposed as its
                discrimination measure \cite{Rignot_1993_TGRS_896}.
Or
                when the MMSE criteria is not very suitable to evaluate
                SAR speckle filters, other criteria likes radiometric
                preservation and speckle suppression power evaluation
                are employed. 
Unfortunately,
                these counter-intuitive measures are not very popular
                outside the SAR community, and newcomers to the field
                are frequently found being trapped by these pitfalls.

%In what way is your solution different ? What is the novelty in your approach and hence solution?
Some of the problems described above have been studied using different approaches in the literature.
However, they have not been presented in a systematic manner nor with a strong underlying foundational theory.
%precise problem statement
Hence the \textbf{main problem statement} of this thesis arises. %it is important to emphasize again the main problem statement of this thesis.
That is,
                this thesis focuses on providing a solution for the
                dual-problem of: 1) establishing scalar and
                representative statistical models for the
                multi-dimensional and inter-correlated POLSAR data and
                2) providing consistent measures of distance for both
                SAR and POLSAR data which allow the benefits of the
                homoskedastic statistical estimation framework to be
                demonstrated.

@@

Thus a significant portion of this research effort focuses on developing a computational framework for simulation, evaluation, processing and classification of target polarimetric signatures.
The benefits of such a framework are many fold.
Firstly, simulation allows one to quickly carry out experiments on small synthesized and well-designed scenarios, without the need for highly expensive satellite imagery.
Secondly, simulation provides ground-truth, without which quantitative evaluation of estimators would have been impossible.
Last but certainly not least, such a framework allow one to apply estimators repeatedly, and results from different estimators can be statistically and reliably compared. For example, this would allow different authors to compare results quantitatively.

@@

%How do you evaluate your solution? 
The
                achievement of the research objectives stated above not only provides
                novel solutions to the stated problem, it also
                illustrates the advantages and beneficial implications
                of the proposed theory.  
Compared
                to existing published techniques, the advantage of the
                proposed theory is qualitative, which does not require
                direct quantitative comparisons.
Instead
                a straightforward binary evaluation would be sufficient.
For
                the POLSAR scalar model, its advantages are that not
                only does it lead to consistent discrimination measures, it
                also generalizes the traditional model for one
                dimensional SAR intensity.
For
                the homoskedastic models, their advantage is that they
                enable an additive and homoskedastic statistical
                framework, which is not only capable of overcoming various
                negative impacts of heteroskedasticity, but also results
                in a single better evaluation criteria that can combine
                and represent many different existing performance
                criteria.

@@

@@

Chapter \ref{chap:lit_survey} will survey the related publications
  and the state-of-the-art techniques in modelling, processing, filtering and evaluating (POL)SAR speckle filter. %will be presented.
It will also discuss the different measures of distance for both SAR and POLSAR data, together with their extensive applications. 
Through these discussions, the need for a homoskedastic and scalar model for the multivariate and heteroskedastic POLSAR is brought forward.

@@

%The heart of is thesis contains several contributions which meet the stated objectives.
                Chapter \ref{chap:sar} begins by by highlighting that SAR
                data are heteroskedastic in the original domain, whereas
                logarithmic transformation converts this into a
                homoskedastic model. 
It
                also drives consistent and homoskedastic measures of
                distance for the one dimensional SAR data.
These
                models for SAR are then validated against real-life
                practical data. (i.e. see Research Contribution \ref{itm:log_transform} to \ref{itm:sar_validation})

>>>>

As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is Polarimetric SAR (POLSAR).
POLSAR is the natural extension of SAR, exploiting the natural polarization property of Electromagnetic (EM) waves.
It extends the SAR acquisition information from the traditional single-channel SAR to multi-channel POLSAR data, corresponding to a different combination of transmitted and received polarizations. Similar to the extension from black-and-white images to colour photography, the polarimetric extension brought about
multi-channel POLSAR data as compared to the traditional one-channel SAR data.

@@

Similarly, heteroskedasticity poses numerous negative impacts on the usual framework of statistical estimation, which most of the time makes use of various different techniques and criteria known to work very well on the usual models.
For example, in modelling, it is very common to use subtractive differences to discriminate and to make decisional inferences. However, for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure.
Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criterion which is probably due to the Gauss Markov theorem.
For SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.

@@

 In
                another thread of study, to combat the negative
                impacts caused by multiplicative and heteroskedastic
                properties for SAR data, experienced researchers in the
                field have developed numerous ingenious ways to tackle
                these issues.
For
                example, when the sense of subtractive distance is not
                consistent for SAR data, the ratio is proposed as its
                discrimination measure \cite{Rignot_1993_TGRS_896}.
Or
                when the MMSE criterion is not very suitable to evaluate
                SAR speckle filters, other criteria likes radiometric
                preservation and speckle suppression power evaluation
                are employed. 
Unfortunately,
                these counter-intuitive measures are not very popular
                outside the SAR community, and newcomers to the field
                are frequently found being trapped by these pitfalls.

%In what way is your solution different ? What is the novelty in your approach and hence solution?
Some of the problems described above have been studied using different approaches in the literature.
However, they have not been presented in a systematic manner nor with precise closed-form mathematical models.
%precise problem statement
Hence the \textbf{main problem statement} of this thesis arises. %it is important to emphasize again the main problem statement of this thesis.
That is,
                this thesis focuses on providing a solution for the
                dual-problem of: 1) establishing scalar and
                representative statistical models for the
                multi-dimensional and inter-correlated POLSAR data and
                2) providing consistent measures of distance for both
                SAR and POLSAR data which allow the benefits of the
                homoskedastic statistical estimation framework to be
                demonstrated.

@@

Thus a significant portion of this research effort focuses on developing a computational framework for simulation, evaluation, processing and classification of target polarimetric signatures.
The benefits of such a framework are manyfold.
Firstly, simulation allows one to quickly carry out experiments on small synthesized and well-designed scenarios, without the need for highly expensive satellite imagery.
Secondly, simulation provides ground-truth, without which quantitative evaluation of estimators would have been impossible.
Last but certainly not least, such a framework allow one to apply estimators repeatedly, and results from different estimators can be statistically and reliably compared. For example, this would allow different authors to compare results quantitatively.

@@

%How do you evaluate your solution? 
%The
%                achievement of the research objectives stated above not only provides
%                novel solutions to the stated problem, it also
%                illustrates the advantages and beneficial implications
%                of the proposed theory.  
Compared
                to existing published techniques, the advantage of the
                proposed models is qualitative, which does not require
                direct quantitative comparisons.
Instead
                a straightforward binary evaluation would be sufficient.
For
                the POLSAR scalar model, its advantages are that not
                only does it lead to consistent discrimination measures, it
                also generalizes the traditional model for one
                dimensional SAR intensity.
For
                the homoskedastic models, their advantage is that they
                enable an additive and homoskedastic statistical
                framework, which is not only capable of overcoming various
                negative impacts of heteroskedasticity, but also results
                in a single better evaluation criteria that can combine
                and represent many different existing performance
                criteria.

@@

The work in this research results in the following list of articles that has been prepared for public communication:

\begin{enumerate}
\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
\item \textbf{SLC SAR speckle filtering using homoskedastic features of logarithmic transformation.}
  T. H. Le, I. V. McLoughlin, K. Y. Lee, and T. Brestchneider.
  In \textit{Proceedings of the 31st Asian Conference on Remote Sensing (ACRS)}, Hanoi, Vietnam, Nov 2010. \cite{Le_2010_ACRS}
\item  \textbf{SAR Fuzzy-MLE Speckle Filter using the Distance Consistency Property in Homoskedastic Log-Transformed Domain.}
  T. H. Le and I. V. McLoughlin. 
  In \textit{Proceedings of the 32nd Asian Conference on Remote Sensing (ACRS)}, Taipei, Taiwan, Nov 2011 \cite{Le_2011_ACRS}
\item \textbf{Scalar and Representative Models for Polarimetric SAR Data.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun,
  re-submitted to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
\item \textbf{Using MSE to evaluate SAR speckle filters.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun.
  submitted to \textit{IET Radar, Sonar \& Navigation}
\end{enumerate}

@@

Chapter \ref{chap:lit_survey} surveys the related publications
  and the state-of-the-art techniques in modelling, processing, filtering and evaluating (POL)SAR speckle filter. %will be presented.
It will also discuss the different measures of distance for both SAR and POLSAR data, together with their extensive applications. 
Through these discussions, the need for a homoskedastic and scalar model for the multivariate and heteroskedastic POLSAR is brought forward.

@@

%The heart of is thesis contains several contributions which meet the stated objectives.
                Chapter \ref{chap:sar} begins by highlighting that SAR
                data are heteroskedastic in the original domain, whereas
                logarithmic transformation converts this into a
                homoskedastic model. 
It
                also drives consistent and homoskedastic measures of
                distance for the one dimensional SAR data.
These
                models for SAR are then validated against real-life
                practical data. (i.e. see Research Contribution \ref{itm:log_transform} to \ref{itm:sar_validation})

### 2014-06-20 4/polsar.tex
auto

In summary, this chapter proposes the determinant of the POLSAR covariance matrix as the scalar and representative observable for the both partial and full polarimetric SAR data.
Out of many different scalar projections of the multi-dimensional POLSAR data, this observable is proposed together with its underlying statistical model, from which consistent discriminant measures are also proposed.
The derived models are shown to be heteroskedastic in the original domain, and logarithmic transformation is shown to convert these into homoskedastic models.
The representative power of the observable is explained in a few different ways.
Firstly, the determinant observable neatly transforms into the representative and widely-used SAR intensity when the dimensional number is collapsed to one, putting the commonly-used statistical models for SAR intensity to fall within this generic proposed models.
Secondly, this observable is also  widely used in existing discrimination measures for POLSAR.
In fact, this chapter also proposes several new discrimination measures for POLSAR,
  which together with the proposed statistical models help to link the existing discriminant measures for POLSAR to the widely-used intensity ratio for SAR.
Thus this theory should help in a wide range of applications, where a single scalar observable is required to represent the complex, multi-dimensional and inter-correlated POLSAR data.
It also builds a bridge allowing  certain existing classes of SAR data processing technique to be applicable towards POLSAR data.
%Such applications are briefly explored in the next chapter. 
The next chapter will briefly explore such applications as well as presents further validation of the proposed models.

>>>>

In summary, this chapter proposes the determinant of the POLSAR covariance matrix as the scalar and representative observable for the both partial and full polarimetric SAR data.
Out of many different scalar projections of the multi-dimensional POLSAR data, this observable is proposed together with its underlying statistical model, from which consistent discriminant measures are also proposed.
The derived models are shown to be heteroskedastic in the original domain, and logarithmic transformation is shown to convert these into homoskedastic models.
The representative power of the observable is explained in a few different ways.
Firstly, the determinant observable neatly transforms into the representative and widely-used SAR intensity when the dimensional number is collapsed to one, putting the commonly-used statistical models for SAR intensity to fall within this generic proposed models.
Secondly, this observable is also  widely used in existing discrimination measures for POLSAR.
In fact, this chapter also proposes several new discrimination measures for POLSAR,
  which together with the proposed statistical models help to link the existing discriminant measures for POLSAR to the widely-used intensity ratio for SAR.
Thus the proposed models should help in a wide range of applications, where a single scalar observable is required to represent the complex, multi-dimensional and inter-correlated POLSAR data.
It also builds a bridge allowing  certain existing classes of SAR data processing technique to be applicable towards POLSAR data.
%Such applications are briefly explored in the next chapter. 
The next chapter will briefly explore such applications as well as presents further validation of the proposed models.

### 2014-06-20 6/conclusional_discussion.tex
auto

\begin{enumerate}
\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
\item \textbf{SLC SAR speckle filtering using homoskedastic features of logarithmic transformation.}
  T. H. Le, I. V. McLoughlin, K. Y. Lee, and T. Brestchneider.
  In \textit{Proceedings of the 31st Asian Conference on Remote Sensing (ACRS)}, Hanoi, Vietnam, Nov 2010. \cite{Le_2010_ACRS}
\item  \textbf{SAR Fuzzy-MLE Speckle Filter using the Distance Consistency Property in Homoskedastic Log-Transformed Domain.}
  T. H. Le and I. V. McLoughlin. 
  In \textit{Proceedings of the 32nd Asian Conference on Remote Sensing (ACRS)}, Taipei, Taiwan, Nov 2011 \cite{Le_2011_ACRS}
\item \textbf{Scalar and Representative Models for Polarimetric SAR Data.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun,
  Being finalized for submission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
\item \textbf{Using MSE to evaluate SAR speckle filters.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun.
  Being finalized for submission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing}
\end{enumerate}

>>>>

\begin{enumerate}
\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
\item \textbf{SLC SAR speckle filtering using homoskedastic features of logarithmic transformation.}
  T. H. Le, I. V. McLoughlin, K. Y. Lee, and T. Brestchneider.
  In \textit{Proceedings of the 31st Asian Conference on Remote Sensing (ACRS)}, Hanoi, Vietnam, Nov 2010. \cite{Le_2010_ACRS}
\item  \textbf{SAR Fuzzy-MLE Speckle Filter using the Distance Consistency Property in Homoskedastic Log-Transformed Domain.}
  T. H. Le and I. V. McLoughlin. 
  In \textit{Proceedings of the 32nd Asian Conference on Remote Sensing (ACRS)}, Taipei, Taiwan, Nov 2011 \cite{Le_2011_ACRS}
\item \textbf{Scalar and Representative Models for Polarimetric SAR Data.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun,
  re-submitted to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
\item \textbf{Using MSE to evaluate SAR speckle filters.}
  T. H. Le, I. V. McLoughlin, and C. H. Vun.
  submitted to \textit{IET Radar, Sonar \& Navigation}
\end{enumerate}
